### 2013-09-26 evaluation/paper.tex
new plots for msrc and pascal

The last set of experiments is on the segmentation dataset MSRC-21 and Pascal
VOC\@.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithms. The results are shown in
figure~\cite{msrc_pascal_curves}, with the top four plots showing results on
MSRC-21, and the bottom four plots showing results on Pascal VOC.

In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. All algorithms achieve the desired suboptimality, at least in the
approximate objective. This suggests that inference is somewhat easier for this
task.

@@

We do not consider SSGD with averaging~\cite{lacoste2012simpler} here, but
found it so produce similar results in tentative experiments. In particular, it
never outperformed SZLJSP.

>>>>

The last set of experiments is on the segmentation dataset MSRC-21 and Pascal
VOC\@.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithms. The results are shown in
figure~\cite{msrc_pascal_curves}, with the top four plots showing results on
MSRC-21, and the bottom four plots showing results on Pascal VOC\@.
First, we notice that all algorithms achieve low (approximate) duality gap, and none
of the algorithms terminates prematurely. Also, all algorithms achieve a similar dual value.
All algorithms achieve similar training errors after convergence.
In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. Solving the QP only every 100 steps in the $n$-slack algorithm significantly slows
down learning here. This is in contrast to the yeast datasets, where the converse was true,
even though both datasets have a similar number of training examples.
Given the outcome described above, we suspect that learning was not affected by approximate
inference too much. We leave a more detailed analysis for Chapter~\ref{ch:exact_learning}.

@@

We do not consider SSGD with averaging~\cite{lacoste2012simpler} here, but
found it so produce results similar to plain SSGD in tentative experiments. In
particular, it never outperformed SZLJSP.
